Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-10 prob.tex
prob.tex \section{\label{sec:Examples-for-QuantumIVPM}Examples for Quantum Interval-valued Probability Measures} Fixing operator types...

\begin{example}{[}Another three-dimensional quantum 6-value interval-valued
probability measure{]}\label{ex:three-dimensional-6-value} Given
$r_{0}\in\left[\frac{1}{3},\frac{1}{2}\right]$, we are going to construct
an interval-valued probability measures for each $r_{0}$, and it
has an empty core whenever $r_{0}\in\left(\frac{5+2\sqrt{2}}{17},\frac{1}{2}\right]$.

Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\necess,\unlikely_{0},\likely_{0},\unlikely_{1},\likely_{1}\right\} $,
where $\unlikely_{0}=\left[1-2r_{0},r_{0}\right]$, $\likely_{0}=\left[1-r_{0},2r_{0}\right]$,
$\unlikely_{1}=\left[2-4r_{0},1-r_{0}\right]$, and $\likely_{1}=\left[r_{0},4r_{0}-1\right]$.
This is well-defined since the left-end is less or equal to the right-end
whenever $r_{0}\ge\frac{1}{3}$. If $\ket{0}$, $\ket{1}$, $\ket{2}$,
$\ket{\ps}$, $\ket{\ms}$, $\ket{0_{\theta,\gamma}^{\perp}}$, and
$\ket{\ps_{\theta,\gamma}^{\perp}}$ are defined as in example~\ref{ex:three-dimensional-4-value},
a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
can be defined as follow: 
\begin{enumerate}
\item $\bar{\mu}(\mathbb{0})=\imposs$ and $\bar{\mu}(\mathbb{1})=\necess.$
\item For the dotted half of the red and green circles in figure~\ref{fig:three-dimensional-4-value},
i.e., whenever $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$,
we define 
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely_{1}\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely_{1}\textrm{ .}
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely_{0}$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely_{0}$. 
\end{enumerate}
We now prove $\bar{\mu}$ has an empty core by contradiction. Assume
there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. We first claim that for all $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=r_{0}$.
On one hand, $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\in\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\left[r_{0},4r_{0}-1\right]$
implies $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\ge r_{0}$.
On the other hand, by figure~\ref{fig:three-dimensional-4-value},
it is easy to see for any neighborhood of $\ket{0_{\theta,\gamma}^{\perp}}$,
these is always a state~$\ket{\psi}$ such that $\mu_{\rho}^{B}\left(\proj{\psi}\right)\in\bar{\mu}\left(\proj{\psi}\right)=\unlikely_{0}$,
i.e., $\mu_{\rho}^{B}\left(\proj{\psi}\right)\le r_{0}$. Because
$\mu_{\rho}^{B}$ is continuous, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=r_{0}$.
Similarly, $\mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=r_{0}$.

@@

0 & = & \det\left(\rho-\lambda\mathbb{1}\right)\\

@@

Hence, the solutions of $\lambda$ are $r_{0}$ and $1-r_{0}\pm\sqrt{\left(1-r_{0}\right)^{2}-4\cdot1\cdot\left(-\frac{1}{4}+\frac{5}{2}r_{0}-\frac{17}{4}r_{0}^{2}-b^{2}\right)}$.

@@

This contradiction implies $\bar{\mu}$ has an empty core when $r_{0}\in\left(\frac{5+2\sqrt{2}}{17},\frac{1}{2}\right]$.

Similar to example~\ref{ex:three-dimensional-4-value}, to verify
$\bar{\mu}$ is a quantum interval-valued probability measure for
$r_{0}\in\left[\frac{1}{3},\frac{1}{2}\right]$, we are going to enumerate
all possible orthonormal bases~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
to verify equation~(\ref{eq:non-additive-vectors}).
\begin{enumerate}
\item When $\ket{\psi_{0}}=\ket{0_{\theta,\gamma}^{\perp}}$ for $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we want to prove $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely_{0}$.
Then, we have 
\begin{equation}
\begin{aligned} & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely_{1}=\left[2-4r_{0},1-r_{0}\right]\\
\subseteq & \left[2-4r_{0},2r_{0}\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\unlikely_{0}=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
 & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely_{0}=\left[1-r_{0},2r_{0}\right]\\
\subseteq & \left[1-r_{0},5r_{0}-1\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\likely_{1}=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
\end{aligned}
\label{eq:case2-2}
\end{equation}
In order to verify $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$,
it is sufficient to prove that if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
then ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or $\theta'=\frac{\pi}{2}$.
This is easy because of equation~(\ref{eq:case2-cross}). Similarly,
when $\ket{\psi_{0}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$, equation~(\ref{eq:non-additive-vectors})
holds. 
\item Otherwise, when $\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$,
and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$ for $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, equation~(\ref{eq:non-additive-vectors})
can easily be verified. 
\begin{equation}
\begin{aligned} & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right)=\likely_{0}=\left[1-r_{0},2r_{0}\right]\\
\subseteq & \left[2-4r_{0},2r_{0}\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\unlikely_{0}=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
\end{aligned}
\label{eq:case3-2}
\end{equation}
\end{enumerate}
\qed\end{example}

>>>>

\begin{example}[Another three-dimensional quantum 6-value interval-valued
probability measure]\label{ex:three-dimensional-6-value} Given
$r_{0}\in\left[\frac{1}{3},\frac{1}{2}\right]$, we are going to construct
an interval-valued probability measures for each $r_{0}$, and it
has an empty core whenever $r_{0}\in\left(\frac{5\tensor*[_{\mathbb{R}}]{+}{}2\sqrt{2}}{17},\frac{1}{2}\right]$.

Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\necess,\unlikely_{0},\likely_{0},\unlikely_{1},\likely_{1}\right\} $,
where $\unlikely_{0}=\left[1\tensor*[_{\mathbb{R}}]{-}{}2r_{0},r_{0}\right]$,
$\likely_{0}=\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{0},2r_{0}\right]$,
$\unlikely_{1}=\left[2\tensor*[_{\mathbb{R}}]{-}{}4r_{0},1\tensor*[_{\mathbb{R}}]{-}{}r_{0}\right]$,
and $\likely_{1}=\left[r_{0},4r_{0}\tensor*[_{\mathbb{R}}]{-}{}1\right]$.
This is well-defined since the left-end is less or equal to the right-end
whenever $r_{0}\ge\frac{1}{3}$. If $\ket{0}$, $\ket{1}$, $\ket{2}$,
$\ket{\ps}$, $\ket{\ms}$, $\ket{0_{\theta,\gamma}^{\perp}}$, and
$\ket{\ps_{\theta,\gamma}^{\perp}}$ are defined as in example~\ref{ex:three-dimensional-4-value},
a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
can be defined as follow: 
\begin{enumerate}
\item $\bar{\mu}(\mathbb{0})=\imposs$ and $\bar{\mu}(\mathbb{1})=\necess.$
\item For the dotted half of the red and green circles in figure~\ref{fig:three-dimensional-4-value},
i.e., whenever $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$,
we define 
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely_{1}\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely_{1}\textrm{ .}
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely_{0}$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely_{0}$. 
\end{enumerate}
We now prove $\bar{\mu}$ has an empty core by contradiction. Assume
there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. We first claim that for all $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=r_{0}$.
On one hand, $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\in\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\left[r_{0},4r_{0}\tensor*[_{\mathbb{R}}]{-}{}1\right]$
implies $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\ge r_{0}$.
On the other hand, by figure~\ref{fig:three-dimensional-4-value},
it is easy to see for any neighborhood of $\ket{0_{\theta,\gamma}^{\perp}}$,
these is always a state~$\ket{\psi}$ such that $\mu_{\rho}^{B}\left(\proj{\psi}\right)\in\bar{\mu}\left(\proj{\psi}\right)=\unlikely_{0}$,
i.e., $\mu_{\rho}^{B}\left(\proj{\psi}\right)\le r_{0}$. Because
$\mu_{\rho}^{B}$ is continuous, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=r_{0}$.
Similarly, $\mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=r_{0}$.

@@

0 & = & \det\left(\rho\tensor*[_{\mathscr{O}}]{-}{}\lambda\mathbb{1}\right)\\

@@

Hence, the solutions of $\lambda$ are $r_{0}$ and $1-r_{0}\pm\sqrt{\left(1-r_{0}\right)^{2}-4\cdot1\cdot\left(-\frac{1}{4}+\frac{5}{2}r_{0}-\frac{17}{4}r_{0}^{2}\mathbb{R}-b^{2}\right)}$.

@@

This contradiction implies $\bar{\mu}$ has an empty core when $r_{0}\in\left(\frac{5\tensor*[_{\mathbb{R}}]{+}{}2\sqrt{2}}{17},\frac{1}{2}\right]$.

Similar to example~\ref{ex:three-dimensional-4-value}, to verify
$\bar{\mu}$ is a quantum interval-valued probability measure for
$r_{0}\in\left[\frac{1}{3},\frac{1}{2}\right]$, we are going to enumerate
all possible orthonormal bases~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
to verify equation~(\ref{eq:non-additive-vectors}).
\begin{enumerate}
\item When $\ket{\psi_{0}}=\ket{0_{\theta,\gamma}^{\perp}}$ for $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we want to prove $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely_{0}$.
Then, we have 
\begin{equation}
\begin{aligned} & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely_{1}=\left[2\tensor*[_{\mathbb{R}}]{-}{}4r_{0},1\tensor*[_{\mathbb{R}}]{-}{}r_{0}\right]\\
\subseteq & \left[2\tensor*[_{\mathbb{R}}]{-}{}4r_{0},2r_{0}\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\unlikely_{0}=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
 & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely_{0}=\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{0},2r_{0}\right]\\
\subseteq & \left[1\tensor*[_{\mathbb{R}}]{-}{}r_{0},5r_{0}\tensor*[_{\mathbb{R}}]{-}{}1\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\likely_{1}=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
\end{aligned}
\label{eq:case2-2}
\end{equation}
In order to verify $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely_{0}$,
it is sufficient to prove that if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
then ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or $\theta'=\frac{\pi}{2}$.
This is easy because of equation~(\ref{eq:case2-cross}). Similarly,
when $\ket{\psi_{0}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$, equation~(\ref{eq:non-additive-vectors})
holds. 
\item Otherwise, when $\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$,
and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$ for $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, equation~(\ref{eq:non-additive-vectors})
can easily be verified. 
\begin{equation}
\begin{aligned} & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right)=\likely_{0}=\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{0},2r_{0}\right]\\
\subseteq & \left[2\tensor*[_{\mathbb{R}}]{-}{}4r_{0},2r_{0}\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\unlikely_{0}=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
\end{aligned}
\label{eq:case3-2}
\end{equation}
\end{enumerate}
\qed\end{example}
